Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-15 ms.tex
starting to re-write discussion of fits with f_1 allowed to vary

Here $\vec{I}$ denotes the vector of observed intensities quoted under
the `IRAS convention': $\vec{I}$ = ($I_{217}$, $I_{353}$, ..., $I_{3000}$). The
likelihood function is given by:

@@

As explained in $\S$\ref{sec:modeling} and $\S$\ref{sec:samp}, our 
full-resolution fits fix the parameters $f_1$, $q_1/q_2$, $\beta_1$, $\beta_2$ 
globally so that only the dust temperatures and SED normalization vary on a 
per-pixel basis. The reason for fixing so many parameters is that, at $6.1'$
FWHM, only five SED measurements are available per pixel.

@@

However, sacrificing angular resolution in order to incorporate 
the \PLANCK~100, 143 GHz bands can allow us to introduce an additional free 
parameter and run our Markov chains in three-dimensional parameter space.

We ran the Markov chains in three dimensions by allowing 
$f_1$ to be a third free parameter. In these chains, we sampled the posterior
given by:

@@

We still employ the likelihood function of Equation \ref{equ:like}, the only
difference being that $f_1$ can vary from proposal to proposal within each 
individual pixel when predicting \{$\tilde{I}_{\nu_i}$\} with Equation 
\ref{eqn:inten}. The prior $P(T_2)$ from Equation \ref{equ:t2prior} remains 
unchanged. The prior on $f_1$ is:

@@

With $\bar{f}_1$=0.0363 and $\sigma_{\bar{f}_1}$=0.003. This is a fairly
stringent prior, but we must restrict the fit from wandering with too much
freedom, as we are attempting to constrain three parameters using an SED
with only seven intensity measurements. To boost S/N, we have performed
the fits using maps smoothed to $1^{\circ}$ resolution.

@@

The resulting full-sky map of $f_1$ is shown in Figure \ref{fig:f1}. Some of 
the most striking features occur near the north Galactic pole, and to 
highlight these regions of unusually high $f_1$, we display the northern
Galactic hemisphere in Lambert projection in Figure \ref{fig:f1}.

>>>>

Here $\vec{I}$ denotes the vector of observed thermal dust intensities quoted 
under the `IRAS convention': $\vec{I}$ = ($I_{217}$, $I_{353}$, ..., 
$I_{3000}$). The likelihood function is given by:

@@

%As explained in $\S$\ref{sec:modeling} and $\S$\ref{sec:samp}, our 
%full-resolution fits fix the parameters $f_1$, $q_1/q_2$, $\beta_1$, $\beta_2$ 
%globally so that only the dust temperatures and SED normalization vary on a 
%per-pixel basis. The reason for fixing so many parameters is that, at $6.1'$
%FWHM, only five SED measurements are available per pixel.

@@

As mentioned in $\S$\ref{sec:modeling}, the combination of high S/N and high 
angular resolution afforded by the \PLANCK~HFI maps provides us with the 
opportunity to allow additional parameters of the two-component model, 
previously fixed by FDS99, to vary spatially. Specifically, we consider
allowing $f_1$ to vary, while maintaining $\beta_1$, $\beta_2$, and $q_1/q_2$
spatially constant. In such fits, there will therefore be three free 
parameters.

% sentence or two about why f_1 is natural parameter to try varying 
% rather than q1/q2 or beta1 or beta2 !!!!!~~!!!

In order for such fits to remain sufficiently constrained with an additional 
free parameter, we consider \PLANCK~maps smoothed to $1^{\circ}$ FWHM to 
boost per-pixel S/N, and pixelize at $N_{side}=64$. We also include DIRBE 
140$\mu$m and 240$\mu$m at degree resolution in the fits with free-$f_1$ fits.

% also we're adding in 100 GHz and 143 GHz, which is something not
% done in full-resolution fits

We run the Markov chains in three dimensions sampling in all three of $f_1$,
$\tilde{I}_{545}$ and $T_2$. We are now sampling the posterior given by:

@@

This posterior still employs the likelihood function of Equation 
\ref{equ:like}, the only difference being that $f_1$ can vary from proposal to 
proposal within each individual pixel when predicting \{$\tilde{I}_{\nu_i}$\} 
with Equation \ref{eqn:inten}. The prior $P(T_2)$ from Equation 
\ref{equ:t2prior} remains unchanged. The prior on $f_1$ is:

@@

With $\bar{f}_1$=0.0363 and $\sigma_{\bar{f}_1}$=0.003. This is a fairly
stringent prior, but we must restrict the fit from wandering with too much
freedom, as we are attempting to constrain three parameters using an SED
with only nine intensity measurements, several of which are quite noisy. 
%To boost S/N, we have performed
%the fits using maps smoothed to $1^{\circ}$ resolution.

@@

The resulting full-sky map of $f_1$ is shown in Figure \ref{fig:f1}. A 
general trend of increasing $f_1$ towards lower Galactic latitudes is 
apparent. The other most salient features are the relatively low
values of $f_1$ in the Polaris flare, and the relatively high $f_1$ values
near the north Galactic pole.

%Some of 
%the most striking features occur near the north Galactic pole, and to 
%highlight these regions of unusually high $f_1$, we display the northern
%Galactic hemisphere in Lambert projection in Figure \ref{fig:f1}.
